\chapter{Actions}

\begin{multicols}{2}

Actions allow you to do stuff!
There are a few ways to go about utilizing the action symbols.

\section{Vector Renders}

If for some reason the Paizo font doesn't work, this will.
They are copies of the font, as an image:

\begin{itemize}
  \item \showmacro{\actionIcon}
  \item \showmacro{\activityTwoIcon}
  \item \showmacro{\activityThreeIcon}
  \item \showmacro{\freeActionIcon}
  \item \showmacro{\reactionIcon}
\end{itemize}

You can also resize it manually like so: \showmacro{\actionIcon[2]}

\section{The Official Font}

Using the official Paizo font is the preferred way of doing things.
It automatically scales as you change font sizes, so you don't have to finagle your sizes as with the vector images above.

\begin{itemize}
  \item \showmacro{\oneAction}
  \item \showmacro{\twoAction}
  \item \showmacro{\threeAction}
  \item \showmacro{\freeAction}
  \item \showmacro{\reaction}
\end{itemize}

There are also environments, especially for use when you're creating characters or monsters.

\hrulefill{}
\begin{verbatim}
\begin{pf-action}{Boop snoot}
You attack their snoot, and it gets booped!
\end{pf-action}
\end{verbatim}
\begin{pf-action}{Boop snoot}
You attack their snoot, and it gets booped!
\end{pf-action}

\hrulefill{}
\begin{verbatim}
\begin{pf-activity2}{Double Boop}
The snoot gets booped twice!  It's pretty cool!
\end{pf-activity2}
\end{verbatim}
\begin{pf-activity2}{Double Boop}
The snoot gets booped twice!  It's pretty cool!
\end{pf-activity2}

\hrulefill{}
\begin{verbatim}
\begin{pf-activity3}{Triple Boop}
ZOMG! THREE BOOPS AT ONCE!!! I mean, you could have used the one action type three times, but this is better.
\end{pf-activity3}
\end{verbatim}
\begin{pf-activity3}{Triple Boop}
ZOMG! THREE BOOPS AT ONCE!!! I mean, you could have used the one action type three times, but this is better.
\end{pf-activity3}

\hrulefill{}
\begin{verbatim}
\begin{pf-freeaction}{Not a Boop}
It's a free action to not boop anything...
\end{pf-freeaction}
\end{verbatim}
\begin{pf-freeaction}{Not a Boop}
It's a free action to not boop anything...
\end{pf-freeaction}

\hrulefill{}
\begin{verbatim}
\begin{pf-reaction}{Anti-Boop}
You're about to get booped, boop them first!
\end{pf-reaction}
\end{verbatim}
\begin{pf-reaction}{Anti-Boop}
You're about to get booped, boop them first!
\end{pf-reaction}

\hrulefill{}
\begin{verbatim}
\begin{pf-misc}{Misc Stuff}
For times you don't have an action associated with an ability, like a spell list or something.
\end{pf-misc}
\end{verbatim}
\begin{pf-misc}{Misc Stuff}
For times you don't have an action associated with an ability, like a spell list or something.
\end{pf-misc}



\end{multicols}

